### 2016-11-29 local-capability-machine.tex
f2 proof in progress

\begin{specification}[Malloc v.2]
  $c_\malloc$ satisfies the specification for malloc iff
\[  
  \begin{aligned}
    &\exists \iota_{\malloc,0} \ldotp \\
    &\quad (\forall \iota' \futurestr \iota_{\malloc,0} \ldotp \forall W,i \ldotp W(i)=\iota' \Rightarrow \iota'.H (\iota'.s) (W) = \iota'.H (\iota'.s ([i \mapsto W(i)]))) \; \land \\
    &\quad \iota_{\malloc,0}.v = \perma \; \land \\
    &\quad (\forall \Phi \in \ExecConfs \ldotp \forall \ms_{\var{footprint}}, \hsframe \in \HeapSegments \ldotp \\
    &\qquad \forall i, n, \size \in \nats \ldotp \forall b,e,a \in \Addrs\ldotp\forall p \in \Perms \ldotp \\
    &\qquad \quad \forall \iota_\malloc \futurestr \iota_{\malloc,0} \land \\
    &\qquad \quad \memheap = \ms_{\var{footprint}} \uplus \hsframe \land\\
    &\qquad \quad \heapSat[\ms_{\var{footprint}}]{n}{[i \mapsto \iota_\malloc]} \land \\
    &\qquad \quad \memreg(r_1) = \size \land \\
    &\qquad \quad \size \geq 0 \land \\
    &\qquad \quad \memreg(r_0) = (p,b,e,a) \land \\
    &\qquad \quad \memreg(\pcreg) = c_\malloc \\ %and this needs to change with ABI.
    &\qquad \quad \Rightarrow \\
    &\qquad \qquad\exists \Phi' \in \ExecConfs \ldotp \exists \ms_{\var{footprint}}', \ms_{\var{alloc}} \in \HeapSegments\ldotp\\
    &\qquad \qquad \quad \exists j \in \nats \ldotp \exists b',e'\in \Addrs \ldotp \exists \iota_\malloc' \in \Regions \ldotp \\
    &\qquad \qquad \qquad \Phi \step[j] \Phi' \land \\
    &\qquad \qquad \qquad \memheap[\Phi']=\ms_{\var{footprint}}' \uplus \hs_{\var{alloc}} \uplus \hsframe \land\\
    &\qquad \qquad \qquad \iota_{\malloc}' \futurewk \iota_\malloc \land \\
    &\qquad \qquad \qquad \heapSat[\ms_{\var{footprint}}']{n-j}{[i \mapsto \iota_\malloc']} \land \\
    &\qquad \qquad \qquad \dom(\hs_{\var{alloc}}) = [b',e'] \land \forall a \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0  \land \\
    &\qquad \qquad \qquad \memreg[\Phi'] = \memreg[\Phi]\update{\pcreg}{\updatePcPerm{(p,b,e,a)}}\update{r_1}{((\rwx,\glob),b',e',b')} \land \\
    &\qquad \qquad \qquad \size - 1 = e'-b' )
  \end{aligned}
\]
\end{specification}
In the specification above $\iota_\malloc'$ is a future region of the initial region that governs malloc.

@@

      \item case: $\npair[n']{\ms_\adv} \in \iota_\malloc'.H (\iota_\malloc'.s) (W)$

@@

      \item case: $\npair[n']{\ms_\adv} \in H^\nwl_{\start_\adv,\addrend_\adv} (\start_\adv,\addrend_\adv) W$

@@

\begin{lemma}
  \label{lem:correctness-f2}
  For all $n \in \nats$
  let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\var{offset-link-flag}) \\
    c_{f2} & \defeq ((\rwx,\glob),\mathtt{f2}-\var{offset-link-flag},\mathtt{2f},\mathtt{f2}) \\
    c_{\var{stk}} & \defeq ((\rwlx,\local),\start_\stk,\addrend_{\adv},\start_\stk-1) \\
    \reg & \in \Regs \\
    m & \defeq \hs_{f2} \uplus 
        \hs_\flag \uplus                
        \ms_{\var{link}} \uplus 
        \hs_\adv \uplus 
        \ms_{\malloc} \uplus 
        \ms_{\var{stk}} \uplus
        \ms_{\var{frame}} 
  \end{align*}
  where 
  \begin{align*}
    &\dom(\hs_{f2}) = [\mathtt{f2}-\var{offset-link-flag},\mathtt{2f}] \\
    &\dom(\hs_\flag) = [\flag,\flag] \\
    &\dom(\ms_\link) = [\link,\link+1]\\
    &\dom(\ms_\stk) = [\start_\stk, \addrend_\stk]\\
    &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
    &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]}
  \end{align*}
  and
  \begin{itemize}
  \item The first address of $\hs_{f2}$ contains a global read-only capability for $\hs_\link$, the second address of $\hs_{f2}$ contains a global read-write capability to $\hs_\flag$, the rest of $\hs_{f2}$ contains the code of $f2$.
  \item $\ms_\flag = [flag \mapsto 0]$
  \item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
  \item $\hs_\adv$ is only instructions and possibly a global read-only capability for $\hs_\link$
  \end{itemize}
  if 
  \[
    (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[n] (\halted,m'),
  \]
  then
  \[
    m'(\flag) = 0
  \]  
\end{lemma}
\begin{proof}[Proof of lemma~\ref{lem:correctness-f2}]
  Let $n$ be given and make the assunptions of the lemma. Consider the execution until just after the jump to $\adv$, i.e.,
  \begin{align*}
    &(\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[k] \\
    &\quad(\reg_0\update{\pcreg}{\updatePcPerm{c_\adv}}\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''},m'')
  \end{align*}
Where 
\[
  m''  \defeq \hs_{f2} \uplus 
        \hs_\flag \uplus                
        \ms_\link \uplus 
        \hs_\adv \uplus 
        \ms_\malloc \uplus 
        \ms_\stk' \uplus
        \ms_{\var{frame}}
\]
Only the stack part of memory has changed. The stack and register-file at this point of execution is illustrated in figure~\ref{fig:f2-stack-before-adv}, where
\begin{itemize}
\item The range of authority for 
  \begin{itemize}
  \item $c_\stk'$ is $[\start_\stk,\addrend_\stk]$ (the entire stack)
  \item $c_\stk''$ is $[\start_\stk'',\addrend_\stk]$ (the unused part of the stack)
  \end{itemize}
  the two stack capabilities have the same permissions as $c_\stk$
\item $c_{f2}'$ points to the return address in f2's code.
\item Notice: $f2$ has no return capability, so $r_0$ was not listed as a private register in the call.
\end{itemize}

\begin{figure}
  \label{fig:f2-stack-before-adv}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Stack} \\
\cline{2-2}
   &         \\
   & $\vdots$ \\
\cline{2-2}
$\start_\stk'':$   & $0$\\
\cline{2-2}
$c_\stk',c_\stk'' \rightarrow$   & $c_\stk'$ \\
\cline{2-2}
   & $c_{f2}'$ \\
\cline{2-2}
$c_{\var{prp}} \rightarrow$   & Restore code \\
   & $\vdots$ \\
\cline{2-2}
   & $1$\\
\cline{2-2}
\end{tabular}
\hspace{1cm}
\begin{tabular}{r |c |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $\updatePcPerm{c_\adv}$\\
\cline{2-2}
$r_0$  &  $c_{\var{prp}}$ \\
\cline{2-2}
$r_1$ & $c_\adv$ \\
\cline{2-2}
$r_{\var{priv},1}$ & $w_{p,1}$\\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}'$ \\
\cline{2-2}
& $0$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{Stack and register-file just after jump to $\adv$.}
\end{figure}
Define 
\begin{enumerate}
\item 
  \begin{align*}
W = \;& [0 \mapsto \iota_{\malloc,0}] \\
    & [1 \mapsto \iota^\sta(\perma,\ms_{f2})]\\ 
    & [2 \mapsto \iota^\sta (\perma,\ms_\flag)]\\
    & [3 \mapsto \iota^\sta (\perma,\ms_\link)]\\
    & [4 \mapsto \iota^\nwl_{\start_\adv,\addrend_\adv} (\perma)]\\
    & [5 \mapsto \iota^\sta (\temp,\ms_\stk'|_{[\start_\stk,\start_\stk''-1]})] \\
    & [6 \mapsto \iota^\pwl_{\start_\stk'' + 1, \addrend_\stk} (\temp)]
  \end{align*}
\lau{The interesting regions here are region 5 and 6. Region 5 governs our private part of the stack whereas region 6 governs the part of the stack we are about to release. I don't think it is strictly needed to make them $\temp$ for this example, but in general it is what we wish to do, so we can revoke them upon return.}
\end{enumerate}

@@

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{pwl}} : \Views \fun \Regions\\
  &\iota_{\start,\addrend}^{\var{pwl}} \defeq \lambda \_ \ldotp(\temp,1,=,H^{\var{pwl}}) \\ \\
  &H^{\var{pwl}} : \States \fun (\Worwk \monnefun \UPred{\HeapSegments})\\
  &H^{\var{pwl}} \; (\start,\addrend) \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi_{\var{wk}}(\hat{W}))
    \end{aligned}
  \right\}
\end{align*}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
\newcommand{\wrev}[1]{\revokeTemp{#1}}

Standard regions for when write local is not allowed:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{nwl}} : \Views \parfun \Regions \\
  &\iota_{\start,\addrend}^{\var{nwl}} \defeq \lambda v \ldotp
    \begin{cases}
      (v,1,=,H^{\var{nwl}}) & v \neq \revoked \\
      \bot & \text{otherwise}
\end{cases}
\\ \\
  &H^{\var{nwl}} : \States \fun (\Worstr \monnefun \UPred{\HeapSegments})\\
  &H^{\var{nwl}} \; (\start,\addrend) \;\hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \\
      &\quad \npair[n-1]{\hs(\addr)} \in \stdvr(\revokeTemp{\xistr(\hat{W})})
    \end{aligned}
  \right\}
\end{align*}

@@

\begin{align*}
    & \readCond{}(\gl)(W) =  \\
    & \quad \begin{aligned}[t]
              \{ \npair{(\start,\addrend)} \mid & \;\exists r \in \var{localityReg}(g,W) \ldotp \\
                        & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
                        & \;\qquad W(r)\nsubeq[n-1] \iota^{\var{pwl}}_{\start',\addrend'}(W(r).v) \}
            \end{aligned}
\end{align*}

@@

\begin{lemma}[Private monotonicity-like property]
  \begin{align*}
    & \forall \hs, n, W, W' \ldotp \\
    & \quad  \heapSat[\hs]{n}{W} \land W' \futurewk \wrev{W} \futurestr W \\
    & \qquad \Rightarrow \exists \hs', \hs_f \ldotp \hs = \hs' \uplus \hs_f \land \heapSat[\hs']{n}{W'}
  \end{align*}
\end{lemma}

@@

>>>>

\begin{specification}[Malloc v.2]
  $c_\malloc$ satisfies the specification for malloc iff
\[  
  \begin{aligned}
    &\exists \iota_{\malloc,0} \ldotp \\
    &\quad (\forall \iota' \futurestr \iota_{\malloc,0} \ldotp \forall W,i \ldotp W(i)=\iota' \Rightarrow \iota'.H (\iota'.s) (W) = \iota'.H (\iota'.s) ([i \mapsto W(i)]) ) \; \land \\
    &\quad \iota_{\malloc,0}.v = \perma \; \land \\
    &\quad (\forall \Phi \in \ExecConfs \ldotp \forall \ms_{\var{footprint}}, \hsframe \in \HeapSegments \ldotp \\
    &\qquad \forall i, n, \size \in \nats \ldotp \forall b,e,a \in \Addrs\ldotp\forall p \in \Perms \ldotp \\
    &\qquad \quad \forall \iota_\malloc \futurestr \iota_{\malloc,0} \land \\
    &\qquad \quad \memheap = \ms_{\var{footprint}} \uplus \hsframe \land\\
    &\qquad \quad \heapSat[\ms_{\var{footprint}}]{n}{[i \mapsto \iota_\malloc]} \land \\
    &\qquad \quad \memreg(r_1) = \size \land \\
    &\qquad \quad \size \geq 0 \land \\
    &\qquad \quad \memreg(r_0) = (p,b,e,a) \land \\
    &\qquad \quad \memreg(\pcreg) = c_\malloc \\ %and this needs to change with ABI.
    &\qquad \quad \Rightarrow \\
    &\qquad \qquad\exists \Phi' \in \ExecConfs \ldotp \exists \ms_{\var{footprint}}', \ms_{\var{alloc}} \in \HeapSegments\ldotp\\
    &\qquad \qquad \quad \exists j \in \nats \ldotp \exists b',e'\in \Addrs \ldotp \exists \iota_\malloc' \in \Regions \ldotp \\
    &\qquad \qquad \qquad \Phi \step[j] \Phi' \land \\
    &\qquad \qquad \qquad \memheap[\Phi']=\ms_{\var{footprint}}' \uplus \hs_{\var{alloc}} \uplus \hsframe \land\\
    &\qquad \qquad \qquad \iota_{\malloc}' \futurewk \iota_\malloc \land \\
    &\qquad \qquad \qquad \heapSat[\ms_{\var{footprint}}']{n-j}{[i \mapsto \iota_\malloc']} \land \\
    &\qquad \qquad \qquad \dom(\hs_{\var{alloc}}) = [b',e'] \land \forall a \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0  \land \\
    &\qquad \qquad \qquad \memreg[\Phi'] = \memreg[\Phi]\update{\pcreg}{\updatePcPerm{(p,b,e,a)}}\update{r_1}{((\rwx,\glob),b',e',b')} \land \\
    &\qquad \qquad \qquad \size - 1 = e'-b' )
  \end{aligned}
\]
\end{specification}
In the specification above $\iota_\malloc'$ is a future region of the initial region that governs malloc.

@@

      \item case: $\npair[n']{\ms_\malloc} \in \iota_\malloc'.H (\iota_\malloc'.s) (W)$ 

@@

      \item case: $\npair[n']{\ms_\adv} \in H^\nwl_{\start_\adv,\addrend_\adv} 1 W$ \label{lem:f1-adv-mem-sat}

@@

\begin{lemma}
  \label{lem:correctness-f2}
  For all $n \in \nats$
  let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\var{offset-link-flag}) \\
    c_{f2} & \defeq ((\rwx,\glob),\mathtt{f2}-\var{offset-link-flag},\mathtt{2f},\mathtt{f2}) \\
    c_{\var{stk}} & \defeq ((\rwlx,\local),\start_\stk,\addrend_{\adv},\start_\stk-1) \\
    \reg & \in \Regs \\
    m & \defeq \hs_{f2} \uplus 
        \hs_\flag \uplus                
        \ms_{\var{link}} \uplus 
        \hs_\adv \uplus 
        \ms_{\malloc} \uplus 
        \ms_{\var{stk}} \uplus
        \ms_{\var{frame}} 
  \end{align*}
  where 
  \begin{align*}
    &\dom(\hs_{f2}) = [\mathtt{f2}-\var{offset-link-flag},\mathtt{2f}] \\
    &\dom(\hs_\flag) = [\flag,\flag] \\
    &\dom(\ms_\link) = [\link,\link+1]\\
    &\dom(\ms_\stk) = [\start_\stk, \addrend_\stk]\\
    &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
    &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]}
  \end{align*}
  and
  \begin{itemize}
  \item The first address of $\hs_{f2}$ contains a global read-only capability for $\hs_\link$, the second address of $\hs_{f2}$ contains a global read-write capability to $\hs_\flag$, the rest of $\hs_{f2}$ contains the code of $f2$.
  \item $\ms_\flag = [flag \mapsto 0]$
  \item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
  \item $\hs_\adv$ is only instructions and possibly a global read-only capability for $\hs_\link$
  \end{itemize}
  if 
  \[
    (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[n] (\halted,m'),
  \]
  then
  \[
    m'(\flag) = 0
  \]  
\end{lemma}
\begin{proof}[Proof of lemma~\ref{lem:correctness-f2}]
  Let $n$ be given and make the assunptions of the lemma. Consider the execution until just after the jump to $\adv$, i.e.,
  \begin{multline*}
    (\reg\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[k] \\
    (\reg_0\update{\pcreg}{\updatePcPerm{c_\adv}}\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''},m'')
  \end{multline*}
Where 
\[
  m''  \defeq \hs_{f2} \uplus 
        \hs_\flag \uplus                
        \ms_\link \uplus 
        \hs_\adv \uplus 
        \ms_\malloc \uplus 
        \ms_\stk' \uplus
        \ms_{\var{frame}}
\]
Only the stack part of memory has changed. The stack and register-file at this point of execution is illustrated in figure~\ref{fig:f2-stack-before-adv}, where
\begin{itemize}
\item The range of authority for 
  \begin{itemize}
  \item $c_\stk'$ is $[\start_\stk,\addrend_\stk]$ (the entire stack)
  \item $c_\stk''$ is $[\start_\stk'',\addrend_\stk]$ (the unused part of the stack)
  \end{itemize}
  the two stack capabilities have the same permissions as $c_\stk$
\item $c_{f2}'$ points to the return address in f2's code.
\item $c_{\var{prp}}$ is a local enter-capability (with authority of all of the stack).
\item Notice: $f2$ has no return capability, so $r_0$ was not listed as a private register in the call.
\end{itemize}
$\start_\stk'':$   & $0$\\
$c_\stk',c_\stk'' \rightarrow$   & $c_\stk'$ \\
   & $c_{f2}'$ \\
$c_{\var{prp}} \rightarrow$   & Restore code \\
   & $1$\\
\begin{tabular}{r |c |}
$\pcreg$ & $\updatePcPerm{c_\adv}$\\
$r_0$  &  $c_{\var{prp}}$ \\
$r_1$ & $c_\adv$ \\
$r_{\var{stk}}$  & $c_{\var{stk}}'$ \\
& $0$ \\
\caption{Stack and register-file just after jump to $\adv$.}
\label{fig:f2-stack-before-adv}
W = \;& [0 \mapsto \iota_{\malloc,0}] \\
    & [1 \mapsto \iota^\sta(\perma,\ms_{f2})]\\ 
    & [2 \mapsto \iota^\sta (\perma,\ms_\flag)]\\
    & [3 \mapsto \iota^\sta (\perma,\ms_\link)]\\
    & [4 \mapsto \iota^\nwl_{\start_\adv,\addrend_\adv} (\perma)]\\
    & [5 \mapsto \iota^\sta (\temp,\ms_\stk'|_{[\start_\stk,\start_\stk''-1]})] \\
    & [6 \mapsto \iota^\pwl_{\start_\stk'', \addrend_\stk} (\temp)]
\lau{The interesting regions here are region 5 and 6. Region 5 governs our private part of the stack whereas region 6 governs the part of the stack we are about to release. I don't think it is strictly needed to make them $\temp$ for this example, but in general it is what we wish to do, so we can revoke them upon return.}
Show
  \npair{(\start_\adv,\addrend_\adv)}\in\readCond{}(\glob)(\iota^\pwl_{\start_\adv,\addrend_\adv})
Which amounts to
\iota^\nwl_{\start_\adv,\addrend_\adv} (\perma) \nsubeq[n-1] \iota^\pwl_{\start_\adv,\addrend_\adv} (\perma)
which is indeed the case. Use this to apply the FTLR to get 
\item $\npair{c_\adv} \in \stder(W)$
  \ms  \defeq \hs_{f2} \uplus 
        \ms_\link \uplus 
        \ms_\malloc \uplus 
        \ms_\stk'
($m''$ without the frame) and show
\item $\heapSat[\ms]{n}{W}$ \lau{The argument here is a bit informal}
  \item For $\hs_{f2}$, $\hs_\flag$, and $\ms_\link$ the regions $\iota^\sta(\perma,\ms_{f2})$,$\iota^\sta (\perma,\ms_\flag)$, and $\iota^\sta (\perma,\ms_\link)$ are designed to respectively accept each of these memory segments.
  \item $\hs_\adv$, showing this case is similar to item \ref{lem:f1-adv-mem-sat} in the proof of Lemma~\ref{lem:correctness-f1}.
  \item $\ms_\malloc$, this case follows from the specification of malloc and the assumption that $\iota_{\malloc,0}$ models $\ms_\malloc$.    
  \item $\ms_\stk'$, here we need to split the memory segment in two and for $n' < n$ argue
    \item case $\npair[n']{\ms_\stk'|_{[\start_\stk, \start_\stk''-1]}} \in H^\sta(\ms_\stk'|_{[\start_\stk,\start_\stk''-1]})$:\\ This region matches only this memory segment.
    \item case $\npair[n']{\ms_\stk'|_{[\start_\stk'', \addrend_\stk]}} \in H_{\start_\stk'', \addrend_\stk}(1)(W)$:\\ Show $\forall a \in [\start_\stk'', \addrend_\stk] \ldotp \ms_\stk'|_{[\start_\stk'', \addrend_\stk]}(a) \in \stdvr(W)$, trivially true since these memory cells contain 0. 
\item $\npair{\reg_0\update{\pcreg}{\updatePcPerm{c_\adv}}\update{r_0}{c_{\var{prp}}}\update{r_1}{c_\adv}\update{r_\stk}{c_\stk''}} \in \stdrr(W)$
    \item case $\npair{c_\stk''} \in \stdvr(W)$: Show:
        \item $\npair{(\start_\stk'', \addrend_\stk)} \in \readCond{}(\local)(W)$ \\
          This amounts to showing 
  \iota^\pwl_{\start_\stk'', \addrend_\stk}(\temp) \nsubeq[n-1] \iota^\pwl_{\start_\stk'', \addrend_\stk}(\temp)
which is indeed the case.
        \item $\npair{(\start_\stk'', \addrend_\stk)} \in \writeCond{}(\iota^\pwl,\local)(W)$\\
This amounts to showing 
  \iota^\pwl_{\start_\stk'', \addrend_\stk}(\temp) \nsupeq[n-1] \iota^\pwl_{\start_\stk'', \addrend_\stk}(\temp)
which is indeed the case.
        \item $\npair{(\rwlx,\start_\stk'', \addrend_\stk)} \in \execCond{}(\local)(W)$ \label{f2:rwlx-exec-case} \\
We will show this case in some detail, the others are similar. \\
Let $n' < n$, $W' \futurewk W$, and $a \in [\start_\stk'', \addrend_\stk]$ be given. Show
  \npair[n']{((\rwlx,\local),\start_\stk'', \addrend_\stk,a)} \in \stder(W')
If we can apply the FTLR at this point, then we are done. SFTS:
  \item $\npair[n']{\start_\stk'', \addrend_\stk} \in \readCond{}(\local)(W')$\\
this amounts to showing
  \iota^\pwl_{\start_\stk'', \addrend_\stk}(\temp) \nsubeq[n'-1] \iota^\pwl_{\start_\stk'', \addrend_\stk}(\temp)
which is indeed the case.
  \item $\npair[n']{\start_\stk'', \addrend_\stk} \in \writeCond{}(\local)(W')$ \\
this amounts to showing
  \iota^\pwl_{\start_\stk'', \addrend_\stk}(\temp) \nsupeq[n'-1] \iota^\pwl_{\start_\stk'', \addrend_\stk}(\temp)
which is indeed the case.
        \item $\npair{(\rwx,\start_\stk'', \addrend_\stk)} \in \execCond{}(\local)(W)$\\
Similar to case~\ref{f2:rwlx-exec-case}
        \item $\npair{(\exec,\start_\stk'', \addrend_\stk)} \in \execCond{}(\local)(W)$\\
Similar to case~\ref{f2:rwlx-exec-case}
    \item case $\npair{c_\adv} \in \stdvr(W)$:\\
     Follows from the FTLR.
    \item case $\npair{c_{\var{prp}}} \in \stdvr(W)$:\\
      Let $n' < n$ and $W' \future W$ be given and show
        \npair[n']{\updatePcPerm{c_{\var{prp}}}} \in \stder(W')
      to this en let $n'' \leq n'$, $\heapSat[\ms']{n''}{W'}$, and $\npair[n'']{\reg'} \in \stdrr$ be given and show
        \npair[n'']{(\reg'\update{\pcreg}{\updatePcPerm{c_{\var{prp}}}},\ms')} \in \observations(W')
      Let $i \leq n''$, $m''$ and $\ms_f$ be given and assume
        (\reg'\update{\pcreg}{\updatePcPerm{c_{\var{prp}}}},\ms'\uplus\ms_f) \step[i]
        (\halted,m'')
      (From $\heapSat[\ms']{n''}{W'}$ we know that that $\ms'$ contains memory segments $\hs_{f2}$, $\hs_\flag$, and $\ms_\stk'|_{[\start_\stk, \start_\stk''-1]}$ (our local part of the stack). The restoration code remains unaltered, and so does the data on the stack, so the execution continues by poping the $c_\stk'$ to $r_\stk$ followed by a pop of $c_{f2}'$ to $\pcreg$. Continuing in $f2$, the restore code is poped off the stack which is the last of the $\mathtt{scall}$ instruction. Now the top word of the stack is poped to $r_1$, and thanks to the world satisfaction, we know that this word is 1. The $\mathtt{assert}$ therefore succeeds making no changes to the memory and afterwards the execution halts.)

Use $\revokeTemp(W') \futurestr W'$. From the private-future memory satisfaction lemma (Lemma~\ref{lem:priv-mono-like}) get $\ms''$ and $\ms_f$ such that

    \item case $r\not\in \{\pcreg,r_0,r_1,r_\stk\}$: $\reg_0(r) = 0$. Trivial.
  \end{enumproof}
\end{enumproof}
to get

@@

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^\pwl : \Views \fun \Regions\\
  &\iota_{\start,\addrend}^\pwl \defeq \lambda v \ldotp
    \begin{cases}
      (v,1,=,H^\pwl_{\start,\addrend}) & v \neq \revoked \\
      \bot & \text{otherwise}
    \end{cases} \\
  &H^\pwl : \Addrs^2 \fun \States \fun (\Worwk \monnefun \UPred{\HeapSegments})\\
  &H^\pwl_{\start,\addrend}\; s \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi_{\var{wk}}(\hat{W}))
    \end{aligned}
  \right\}
\end{align*}
\lau{What is the reason to have the ``view'' always be $\temp$? It seems like it does not play well with the read condition if it is always $\temp$.}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
\newcommand{\wrev}[1]{\revokeTemp{#1}}

Standard regions for when write local is not allowed:
\begin{align*}
  &\iota_{\start,\addrend}^{\var{nwl}} : \Views \parfun \Regions \\
  &\iota_{\start,\addrend}^{\var{nwl}} \defeq \lambda v \ldotp
    \begin{cases}
      (v,1,=,H^\nwl_{start,\addrend}) & v \neq \revoked \\
      \bot & \text{otherwise}
\end{cases}
\\ \\
  &H^\nwl : \Addrs^2 \fun \States \fun (\Worstr \monnefun \UPred{\HeapSegments})\\
  &H^\nwl_{\start,\addrend} \; s \;\hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \\
      &\quad \npair[n-1]{\hs(\addr)} \in \stdvr(\revokeTemp{\xistr(\hat{W})})
    \end{aligned}
  \right\}
\end{align*}

@@

\begin{align*}
    & \readCond{}(\gl)(W) =  \\
    & \quad \begin{aligned}[t]
              \{ \npair{(\start,\addrend)} \mid & \;\exists r \in \var{localityReg}(g,W) \ldotp \\
                        & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
                        & \;\qquad W(r)\nsubeq[n-1] \iota^\pwl_{\start',\addrend'}(W(r).v) \}
            \end{aligned}
\end{align*}

@@

\begin{lemma}[Private monotonicity-like property]
\label{lem:priv-mono-like}
  \begin{align*}
    & \forall \hs, n, W, W' \ldotp \\
    & \quad  \heapSat[\hs]{n}{W} \land W' \futurewk \wrev{W} \futurestr W \\
    & \qquad \Rightarrow \exists \hs', \hs_f \ldotp \hs = \hs' \uplus \hs_f \land \heapSat[\hs']{n}{W'}
  \end{align*}
\end{lemma}

@@

\subsubsection{Standard regions}
\begin{lemma}
  \begin{align*}
    & \forall n \in \nats\ldotp \forall \addr, \addrend \in \Addrs \ldotp \forall v \in \{\perma, \temp\} \ldotp \\
    & \quad \iota^\nwl_{\start,\addrend} (v) \nsubeq \iota^\pwl_{\start,\addrend}(v)
  \end{align*}
\end{lemma}
